### 2019-07-31 thesis.tex
better days will come

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
  brief, but comprehensive, description of the scales and characteristics of
  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter in the universe is in the plasma state\cite{may}. Under
cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
around galaxies or in the atmosphere of cold stars have a strong reaction to
electromagnetic fields, exhibiting the characteristic collective behavior of
plasmas\cite{tsypa,peratt2014}.
Since this ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been increasingly exchanging knowledge, with plasma
physics providing theoretical background, computational and laboratory models
that might help with the interpretation and physical explanation of astrophysical
observations, and astrophysics confirming theoretical and computational
predictions on plasma physics with observations of phenomena that are unique
to space plasma\cite{tsypa,Kulsrud2005}.

On that regard, the results obtained during this graduate research can be
found on both sides of this mutual contribution. In \cite{Tigik2016a},
\cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
numerical evidence of plasma processes that might aid in the interpretation
and accurate modeling  of phenomena observed in the solar plasma. While in
\cite{Tigik2017a}, we introduce a new equation depicting an unknown process
and numerically analyze it in the context of solar physics; its existence
outside theory, however, will depend on the development of more advanced
space probes to be confirmed. The choice for applying our theory to
phenomena observed in the solar plasma, and not in some remote space plasma,
now became evident. The accessibility to direct, in situ measurements,
highly resolved remote sensing and high-resolution spectroscopy made the
solar plasma the right choice for our analysis.

@@

\section{Solar physics}
\label{sec:solar-physics}

@@

>>>>

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
  brief, but comprehensive, description of the scales and characteristics of
  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter in the universe is in the plasma state\cite{may}. Under
cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
around galaxies or in the atmosphere of cold stars have a strong reaction to
electromagnetic fields, exhibiting the characteristic collective behavior of
plasmas\cite{tsypa,peratt2014}.

Since the ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been noticing an increasing necessity for exchanging
knowledge and mutually collaborating with their results. In this arrangement,
plasma physics provides theoretical, computational, and laboratory models
that might help with the interpretation and propose a physical explanation
for astrophysical observations. Astrophysics, on the other hand, contributes
with data from observations of phenomena that are unique to cosmic plasma and
might be used to confirm theoretical and computational predictions on plasma
physics, and also to compare with experimental results\cite{tsypa,Kulsrud2005}.
A particular field of research that has been acting for a long time as a bridge
between these two areas is the solar physics.

@@

\section{Solar and space physics}
\label{sec:solar-physics}
Solar physics can be thought of as a combination of plasma and space physics.
The wide variety of plasmas and the accessibility to direct, in situ measurements,
highly resolved remote sensing and high-resolution spectroscopy turned the solar
system into Earth's plasma physics laboratory in space.
%% falar sobre como física sola pode contribuir para fśica de plasmas em geral

@@

% The theory developed during this graduate research makes use of solar physics
% results to contribute on both sides. In \cite{Tigik2016a},
% \cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
% numerical evidence of plasma processes that might aid in the interpretation
% and accurate modeling  of phenomena observed in the solar plasma. While in
% \cite{Tigik2017a}, we introduce a new equation depicting an unknown process
% and numerically analyze it in the context of solar physics; its existence
% outside theory, however, will depend on the development of more advanced
% space probes to be confirmed.
